---
title: "Greek Debt Crisis"
author: "Artem"
date: "2025-02-14"
output: html_document
---

```{r}

library(rvest)
library(xml2)
library(stringr)
library(httr)
library(jsonlite)
library(lubridate)
library(tidyverse)
library(openxlsx)
library(readxl)
library(syuzhet)

```

***Part I - Data Extraction***

1.1.1 El País (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyElPaisGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ElPaisGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  ElPaisGreeceOutputList <- fromJSON(content(ElPaisGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(ElPaisGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  ElPaisGreeceHeadlines <- as.data.frame(ElPaisGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  colnames(ElPaisGreeceHeadlines) <- ElPaisGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredElPaisGreeceHeadlines <- ElPaisGreeceHeadlines[
    substr(ElPaisGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredElPaisGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  RandomElPaisGreeceHeadline <- FilteredElPaisGreeceHeadlines[
    sample(1:nrow(FilteredElPaisGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomElPaisGreeceHeadline$timestamp
  OriginalElPaisGreeceURL <- RandomElPaisGreeceHeadline$urlkey
  
  RegularElPaisGreeceURL <- gsub("com,elpais)/", "elpais.com/", OriginalElPaisGreeceURL, fixed = TRUE) 
  
  RetrievedElPaisGreeceURL <- paste0("https://web.archive.org/web/",
                                     TimestampGreece, "/",
                                     RegularElPaisGreeceURL)
  
  cat("Retrieved from El País:", RetrievedElPaisGreeceURL, "\n")
  
  return(RetrievedElPaisGreeceURL)
}

GreeceSpanishVectorOfWords <- c("Grecia", "griego", "griega")

ElPaisGreeceDynamicDataFrame <- data.frame(ElPaisGreeceDate = character(0),
                                           ElPaisGreeceHeadline = character(0),
                                           ElPaisGreeceWeighting = numeric(0),
                                           ElPaisGreeceTag = character(0))

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ElPaisGreeceTargetURL <- DailyElPaisGreeceHeadline("www.elpais.com", CurrentDateGreece) 
  
  if (is.na(ElPaisGreeceTargetURL)) next
  
  ElPaisGreeceWebsite <- read_html(ElPaisGreeceTargetURL)
  
  ElPaisGreeceMaxWeighting <- 0
  ElPaisGreeceMaxWeightingRow <- NULL
  
  for (ElPaisGreeceTag in c("h1", "h2", "h3")) {
    ElPaisGreeceHeadlines <- ElPaisGreeceWebsite %>% html_nodes(ElPaisGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (ElPaisGreeceHeadline in ElPaisGreeceHeadlines) {
      GreeceSpanishVectorOfWordsMatch <- any(str_detect(
        ElPaisGreeceHeadline, regex(paste(GreeceSpanishVectorOfWords, collapse = "|"), ignore_case = TRUE)
      ))
      
      if (GreeceSpanishVectorOfWordsMatch) {
        ElPaisGreeceRawWeighting <- length(ElPaisGreeceHeadlines) - 
          match(ElPaisGreeceHeadline, ElPaisGreeceHeadlines) + 1
        ElPaisGreeceNormalisedWeighting <- ElPaisGreeceRawWeighting / length(ElPaisGreeceHeadlines) 

        if (ElPaisGreeceNormalisedWeighting > ElPaisGreeceMaxWeighting) {
          ElPaisGreeceMaxWeighting <- ElPaisGreeceNormalisedWeighting
          ElPaisGreeceMaxWeightingRow <- data.frame(
            ElPaisGreeceDate = as.character(CurrentDateGreece),
            ElPaisGreeceHeadline = ElPaisGreeceHeadline,
            ElPaisGreeceWeighting = ElPaisGreeceNormalisedWeighting, 
            ElPaisGreeceTag = ElPaisGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(ElPaisGreeceMaxWeightingRow)) {
    ElPaisGreeceDynamicDataFrame <- rbind(ElPaisGreeceDynamicDataFrame, ElPaisGreeceMaxWeightingRow)
  } else {
    ElPaisGreeceNARow <- data.frame(
      ElPaisGreeceDate = as.character(CurrentDateGreece),
      ElPaisGreeceHeadline = NA,
      ElPaisGreeceWeighting = 0,
      ElPaisGreeceTag = NA
    )
    ElPaisGreeceDynamicDataFrame <- rbind(ElPaisGreeceDynamicDataFrame, ElPaisGreeceNARow)
  }
}

head(ElPaisGreeceDynamicDataFrame)
tail(ElPaisGreeceDynamicDataFrame)

```

```{r}

write.xlsx(ElPaisGreeceDynamicDataFrame, "ElPaisGreece2011.xlsx")

```


1.1.2 El País (2015)

```{r}

StartDateGreece <- as.Date("2015-01-27")

DailyElPaisGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ElPaisGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
                query = list(url = domain, timestamp = format(date, "%Y%m%d"),
                             output = "json"), times = 90, pause_cap = RandomPauseCap)
  
  ElPaisGreeceOutputList <-
    fromJSON(content(ElPaisGreeceOutputURL, "text", encoding = "UTF-8"))
  
  ElPaisGreeceHeadlines <- as.data.frame(ElPaisGreeceOutputList[-1, ],
                                       stringsAsFactors = FALSE)
  
  colnames(ElPaisGreeceHeadlines) <- ElPaisGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredElPaisGreeceHeadlines <-
  ElPaisGreeceHeadlines[grepl(DesiredDateGreece, ElPaisGreeceHeadlines$timestamp,
                                  fixed = TRUE), ]
  
  RandomElPaisGreeceHeadline <-
    FilteredElPaisGreeceHeadlines[sample(1:nrow(FilteredElPaisGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomElPaisGreeceHeadline$timestamp
  
  OriginalElPaisGreeceURL <- RandomElPaisGreeceHeadline$urlkey
  
  RegularElPaisGreeceURL <- gsub("com,elpais)/", "elpais.com/",
                                OriginalElPaisGreeceURL, fixed = TRUE) 
  
  RetrievedElPaisGreeceURL <- paste0("https://web.archive.org/web/",
                                   TimestampGreece, "/",
                                    RegularElPaisGreeceURL)
  
  cat("Retrieved from El País:", RetrievedElPaisGreeceURL, "\n")
  
  return(RetrievedElPaisGreeceURL)
}

GreeceSpanishVectorOfWords <- c("Grecia", "griego", "griega")

ElPaisGreeceDynamicDataFrame <- data.frame(ElPaisGreeceDate = character(0),
                                          ElPaisGreeceHeadline = character(0),
                                          ElPaisGreeceWeighting = numeric(0),
                                          ElPaisGreeceTag = character(0))

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ElPaisGreeceTargetURL <- DailyElPaisGreeceHeadline("www.elpais.com",
                                                   CurrentDateGreece) 
  
  ElPaisGreeceWebsite <- read_html(ElPaisGreeceTargetURL)
  
  ElPaisGreeceMaxWeighting <- 0
  ElPaisGreeceMaxWeightingRow <- NULL
  
  for (ElPaisGreeceTag in c("h1", "h2", "h3")) {
    ElPaisGreeceHeadlines <- ElPaisGreeceWebsite %>% html_nodes(ElPaisGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (ElPaisGreeceHeadline in ElPaisGreeceHeadlines) {
      GreeceSpanishVectorOfWordsMatch <- any(str_detect(ElPaisGreeceHeadline, regex(paste(GreeceSpanishVectorOfWords, collapse = "|"),
                                                         ignore_case = TRUE)))
      
      if (GreeceSpanishVectorOfWordsMatch) {
        ElPaisGreeceRawWeighting <-
          length(ElPaisGreeceHeadlines) - match(ElPaisGreeceHeadline,
                                              ElPaisGreeceHeadlines) + 1
        ElPaisGreeceNormalisedWeighting <- ElPaisGreeceRawWeighting / length(ElPaisGreeceHeadlines) 

        if (ElPaisGreeceNormalisedWeighting > ElPaisGreeceMaxWeighting) {
          ElPaisGreeceMaxWeighting <- ElPaisGreeceNormalisedWeighting
          ElPaisGreeceMaxWeightingRow <- data.frame(ElPaisGreeceDate =
                                                    as.character(CurrentDateGreece),
                                                   ElPaisGreeceHeadline =
                                                    ElPaisGreeceHeadline,
                                                   ElPaisGreeceWeighting = 
                                                    ElPaisGreeceNormalisedWeighting, 
                                                   ElPaisGreeceTag = ElPaisGreeceTag)
        }
      }
    }
  }
  
  if (!is.null(ElPaisGreeceMaxWeightingRow)) {
    ElPaisGreeceDynamicDataFrame <- rbind(ElPaisGreeceDynamicDataFrame, ElPaisGreeceMaxWeightingRow)
  } else {
    ElPaisGreeceNARow <-
      data.frame(ElPaisGreeceDate = as.character(CurrentDateGreece),
                                   ElPaisGreeceHeadline = NA,
                                   ElPaisGreeceWeighting = 0,
                                   ElPaisGreeceTag = NA)
    ElPaisGreeceDynamicDataFrame <- rbind(ElPaisGreeceDynamicDataFrame,
                                         ElPaisGreeceNARow)
  }
}

head(ElPaisGreeceDynamicDataFrame)
tail(ElPaisGreeceDynamicDataFrame)

```

```{r}

write.xlsx(ElPaisGreeceDynamicDataFrame, "ElPaisGreece2015.xlsx")

```


1.2.1 El Mundo (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyElMundoGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ElMundoGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  ElMundoGreeceOutputList <- fromJSON(content(ElMundoGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(ElMundoGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  ElMundoGreeceHeadlines <- as.data.frame(ElMundoGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  colnames(ElMundoGreeceHeadlines) <- ElMundoGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredElMundoGreeceHeadlines <- ElMundoGreeceHeadlines[
    substr(ElMundoGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredElMundoGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  RandomElMundoGreeceHeadline <- FilteredElMundoGreeceHeadlines[
    sample(1:nrow(FilteredElMundoGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomElMundoGreeceHeadline$timestamp
  OriginalElMundoGreeceURL <- RandomElMundoGreeceHeadline$urlkey
  
  RegularElMundoGreeceURL <- gsub("es,elmundo)/", "elmundo.es/", OriginalElMundoGreeceURL, fixed = TRUE) 
  
  RetrievedElMundoGreeceURL <- paste0("https://web.archive.org/web/",
                                     TimestampGreece, "/",
                                     RegularElMundoGreeceURL)
  
  cat("Retrieved from El Mundo:", RetrievedElMundoGreeceURL, "\n")
  
  return(RetrievedElMundoGreeceURL)
}

GreeceSpanishVectorOfWords <- c("Grecia", "griego", "griega")

ElMundoGreeceDynamicDataFrame <- data.frame(ElMundoGreeceDate = character(0),
                                           ElMundoGreeceHeadline = character(0),
                                           ElMundoGreeceWeighting = numeric(0),
                                           ElMundoGreeceTag = character(0))

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ElMundoGreeceTargetURL <- DailyElMundoGreeceHeadline("www.elmundo.es", CurrentDateGreece) 
  
  if (is.na(ElMundoGreeceTargetURL)) next
  
  ElMundoGreeceWebsite <- read_html(ElMundoGreeceTargetURL)
  
  ElMundoGreeceMaxWeighting <- 0
  ElMundoGreeceMaxWeightingRow <- NULL
  
  for (ElMundoGreeceTag in c("h1", "h2", "h3")) {
    ElMundoGreeceHeadlines <- ElMundoGreeceWebsite %>% html_nodes(ElMundoGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (ElMundoGreeceHeadline in ElMundoGreeceHeadlines) {
      GreeceSpanishVectorOfWordsMatch <- any(str_detect(
        ElMundoGreeceHeadline, regex(paste(GreeceSpanishVectorOfWords, collapse = "|"), ignore_case = TRUE)
      ))
      
      if (GreeceSpanishVectorOfWordsMatch) {
        ElMundoGreeceRawWeighting <- length(ElMundoGreeceHeadlines) - 
          match(ElMundoGreeceHeadline, ElMundoGreeceHeadlines) + 1
        ElMundoGreeceNormalisedWeighting <- ElMundoGreeceRawWeighting / length(ElMundoGreeceHeadlines) 

        if (ElMundoGreeceNormalisedWeighting > ElMundoGreeceMaxWeighting) {
          ElMundoGreeceMaxWeighting <- ElMundoGreeceNormalisedWeighting
          ElMundoGreeceMaxWeightingRow <- data.frame(
            ElMundoGreeceDate = as.character(CurrentDateGreece),
            ElMundoGreeceHeadline = ElMundoGreeceHeadline,
            ElMundoGreeceWeighting = ElMundoGreeceNormalisedWeighting, 
            ElMundoGreeceTag = ElMundoGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(ElMundoGreeceMaxWeightingRow)) {
    ElMundoGreeceDynamicDataFrame <- rbind(ElMundoGreeceDynamicDataFrame, ElMundoGreeceMaxWeightingRow)
  } else {
    ElMundoGreeceNARow <- data.frame(
      ElMundoGreeceDate = as.character(CurrentDateGreece),
      ElMundoGreeceHeadline = NA,
      ElMundoGreeceWeighting = 0,
      ElMundoGreeceTag = NA
    )
    ElMundoGreeceDynamicDataFrame <- rbind(ElMundoGreeceDynamicDataFrame, ElMundoGreeceNARow)
  }
}

head(ElMundoGreeceDynamicDataFrame)
tail(ElMundoGreeceDynamicDataFrame)

```


```{r}

write.xlsx(ElMundoGreeceDynamicDataFrame, "ElMundoGreece2011.xlsx")

```


1.2.2 El Mundo (2015)

```{r}

StartDateGreece <- as.Date("2015-01-27")

DailyElMundoGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ElMundoGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
                query = list(url = domain, timestamp = format(date, "%Y%m%d"),
                             output = "json"), times = 90, pause_cap = RandomPauseCap)
  
  ElMundoGreeceOutputList <-
    fromJSON(content(ElMundoGreeceOutputURL, "text", encoding = "UTF-8"))
  
  ElMundoGreeceHeadlines <- as.data.frame(ElMundoGreeceOutputList[-1, ],
                                       stringsAsFactors = FALSE)
  
  colnames(ElMundoGreeceHeadlines) <- ElMundoGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredElMundoGreeceHeadlines <-
  ElMundoGreeceHeadlines[grepl(DesiredDateGreece, ElMundoGreeceHeadlines$timestamp,
                                  fixed = TRUE), ]
  
  RandomElMundoGreeceHeadline <-
    FilteredElMundoGreeceHeadlines[sample(1:nrow(FilteredElMundoGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomElMundoGreeceHeadline$timestamp
  
  OriginalElMundoGreeceURL <- RandomElMundoGreeceHeadline$urlkey
  
  RegularElMundoGreeceURL <- gsub("es,elmundo)/", "elmundo.es/",
                                OriginalElMundoGreeceURL, fixed = TRUE) 
  
  RetrievedElMundoGreeceURL <- paste0("https://web.archive.org/web/",
                                   TimestampGreece, "/",
                                    RegularElMundoGreeceURL)
  
  cat("Retrieved from El Mundo:", RetrievedElMundoGreeceURL, "\n")
  
  return(RetrievedElMundoGreeceURL)
}

GreeceSpanishVectorOfWords <- c("Grecia", "griego", "griega")

ElMundoGreeceDynamicDataFrame <- data.frame(ElMundoGreeceDate = character(0),
                                          ElMundoGreeceHeadline = character(0),
                                          ElMundoGreeceWeighting = numeric(0),
                                          ElMundoGreeceTag = character(0))

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ElMundoGreeceTargetURL <- DailyElMundoGreeceHeadline("www.elmundo.es",
                                                   CurrentDateGreece) 
  
  ElMundoGreeceWebsite <- read_html(ElMundoGreeceTargetURL)
  
  ElMundoGreeceMaxWeighting <- 0
  ElMundoGreeceMaxWeightingRow <- NULL
  
  for (ElMundoGreeceTag in c("h1", "h2", "h3")) {
    ElMundoGreeceHeadlines <- ElMundoGreeceWebsite %>% html_nodes(ElMundoGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (ElMundoGreeceHeadline in ElMundoGreeceHeadlines) {
      GreeceSpanishVectorOfWordsMatch <- any(str_detect(ElMundoGreeceHeadline, regex(paste(GreeceSpanishVectorOfWords, collapse = "|"),
                                                         ignore_case = TRUE)))
      
      if (GreeceSpanishVectorOfWordsMatch) {
        ElMundoGreeceRawWeighting <-
          length(ElMundoGreeceHeadlines) - match(ElMundoGreeceHeadline,
                                              ElMundoGreeceHeadlines) + 1
        ElMundoGreeceNormalisedWeighting <- ElMundoGreeceRawWeighting / length(ElMundoGreeceHeadlines) 

        if (ElMundoGreeceNormalisedWeighting > ElMundoGreeceMaxWeighting) {
          ElMundoGreeceMaxWeighting <- ElMundoGreeceNormalisedWeighting
          ElMundoGreeceMaxWeightingRow <- data.frame(ElMundoGreeceDate =
                                                    as.character(CurrentDateGreece),
                                                   ElMundoGreeceHeadline =
                                                    ElMundoGreeceHeadline,
                                                   ElMundoGreeceWeighting = 
                                                    ElMundoGreeceNormalisedWeighting, 
                                                   ElMundoGreeceTag = ElMundoGreeceTag)
        }
      }
    }
  }
  
  if (!is.null(ElMundoGreeceMaxWeightingRow)) {
    ElMundoGreeceDynamicDataFrame <- rbind(ElMundoGreeceDynamicDataFrame, ElMundoGreeceMaxWeightingRow)
  } else {
    ElMundoGreeceNARow <-
      data.frame(ElMundoGreeceDate = as.character(CurrentDateGreece),
                                   ElMundoGreeceHeadline = NA,
                                   ElMundoGreeceWeighting = 0,
                                   ElMundoGreeceTag = NA)
    ElMundoGreeceDynamicDataFrame <- rbind(ElMundoGreeceDynamicDataFrame,
                                         ElMundoGreeceNARow)
  }
}

head(ElMundoGreeceDynamicDataFrame)
tail(ElMundoGreeceDynamicDataFrame)

```

```{r}

write.xlsx(ElMundoGreeceDynamicDataFrame, "ElMundoGreece2015.xlsx")

```



1.3.1 Corriere della Sera (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyCDSGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  CDSGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  CDSGreeceOutputList <- fromJSON(content(CDSGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(CDSGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(CDSGreeceOutputList) || ncol(CDSGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- CDSGreeceOutputList[1, ]
  CDSGreeceHeadlines <- as.data.frame(CDSGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(CDSGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(CDSGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredCDSGreeceHeadlines <- CDSGreeceHeadlines[
    substr(CDSGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredCDSGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidCDSGreeceHeadlines <- FilteredCDSGreeceHeadlines[
    FilteredCDSGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredCDSGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidCDSGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidCDSGreeceHeadlines)) {
    RandomCDSGreeceHeadline <- ValidCDSGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomCDSGreeceHeadline$timestamp
    OriginalCDSGreeceURL <- RandomCDSGreeceHeadline$urlkey
    
    RegularCDSGreeceURL <- gsub("it,corriere)/", "corriere.it/", OriginalCDSGreeceURL, fixed = TRUE) 
    
    RetrievedCDSGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularCDSGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedCDSGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from CDS:", RetrievedCDSGreeceURL, "\n")
      return(RetrievedCDSGreeceURL)
    } else {
      cat("Snapshot", RetrievedCDSGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreeceItalianVectorOfWords <- c("grec")

CDSGreeceDynamicDataFrame <- data.frame(
  CDSGreeceDate = character(0),
  CDSGreeceHeadline = character(0),
  CDSGreeceWeighting = numeric(0),
  CDSGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  CDSGreeceTargetURL <- DailyCDSGreeceHeadline("www.corriere.it", CurrentDateGreece) 
  
  if (is.na(CDSGreeceTargetURL)) next
  
  CDSGreeceWebsite <- read_html(CDSGreeceTargetURL)
  
  CDSGreeceMaxWeighting <- 0
  CDSGreeceMaxWeightingRow <- NULL
  
  for (CDSGreeceTag in c("h1", "h2", "h3")) {
    CDSGreeceHeadlines <- CDSGreeceWebsite %>% html_nodes(CDSGreeceTag) %>% html_text(trim = TRUE)
    
    for (CDSGreeceHeadline in CDSGreeceHeadlines) {
      if (any(str_detect(CDSGreeceHeadline, regex(paste(GreeceItalianVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        CDSGreeceRawWeighting <- length(CDSGreeceHeadlines) - match(CDSGreeceHeadline, CDSGreeceHeadlines) + 1
        CDSGreeceNormalisedWeighting <- CDSGreeceRawWeighting / length(CDSGreeceHeadlines)
        
        if (CDSGreeceNormalisedWeighting > CDSGreeceMaxWeighting) {
          CDSGreeceMaxWeighting <- CDSGreeceNormalisedWeighting
          CDSGreeceMaxWeightingRow <- data.frame(
            CDSGreeceDate = as.character(CurrentDateGreece),
            CDSGreeceHeadline = CDSGreeceHeadline,
            CDSGreeceWeighting = CDSGreeceNormalisedWeighting,
            CDSGreeceTag = CDSGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(CDSGreeceMaxWeightingRow)) {
    CDSGreeceDynamicDataFrame <- rbind(CDSGreeceDynamicDataFrame, CDSGreeceMaxWeightingRow)
  } else {
    CDSGreeceNARow <- data.frame(
      CDSGreeceDate = as.character(CurrentDateGreece),
      CDSGreeceHeadline = NA,
      CDSGreeceWeighting = 0,
      CDSGreeceTag = NA
    )
    CDSGreeceDynamicDataFrame <- rbind(CDSGreeceDynamicDataFrame, CDSGreeceNARow)
  }
}

head(CDSGreeceDynamicDataFrame)
tail(CDSGreeceDynamicDataFrame)

```

```{r}

write.xlsx(CDSGreeceDynamicDataFrame, "CorriereGreece2011.xlsx")

```



1.3.2 Corriere della Sera (2015)

```{r}

StartDateGreece <- as.Date("2015-03-03")

DailyCDSGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  CDSGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
                query = list(url = domain, timestamp = format(date, "%Y%m%d"),
                             output = "json"), times = 90, pause_cap = RandomPauseCap)
  
  CDSGreeceOutputList <-
    fromJSON(content(CDSGreeceOutputURL, "text", encoding = "UTF-8"))
  
  CDSGreeceHeadlines <- as.data.frame(CDSGreeceOutputList[-1, ],
                                       stringsAsFactors = FALSE)
  
  colnames(CDSGreeceHeadlines) <- CDSGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredCDSGreeceHeadlines <-
  CDSGreeceHeadlines[grepl(DesiredDateGreece, CDSGreeceHeadlines$timestamp,
                                  fixed = TRUE), ]
  
  RandomCDSGreeceHeadline <-
    FilteredCDSGreeceHeadlines[sample(1:nrow(FilteredCDSGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomCDSGreeceHeadline$timestamp
  
  OriginalCDSGreeceURL <- RandomCDSGreeceHeadline$urlkey
  
  RegularCDSGreeceURL <- gsub("it,corriere)/", "corriere.it/",
                                OriginalCDSGreeceURL, fixed = TRUE) 
  
  RetrievedCDSGreeceURL <- paste0("https://web.archive.org/web/",
                                   TimestampGreece, "/",
                                    RegularCDSGreeceURL)
  
  cat("Retrieved from CDS:", RetrievedCDSGreeceURL, "\n")
  
  return(RetrievedCDSGreeceURL)
}

GreeceItalianVectorOfWords <- c("grec")

CDSGreeceDynamicDataFrame <- data.frame(CDSGreeceDate = character(0),
                                          CDSGreeceHeadline = character(0),
                                          CDSGreeceWeighting = numeric(0),
                                          CDSGreeceTag = character(0))

for (i in 0:1) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  CDSGreeceTargetURL <- DailyCDSGreeceHeadline("www.corriere.it",
                                                   CurrentDateGreece) 
  
  CDSGreeceWebsite <- read_html(CDSGreeceTargetURL)
  
  CDSGreeceMaxWeighting <- 0
  CDSGreeceMaxWeightingRow <- NULL
  
  for (CDSGreeceTag in c("h1", "h2", "h3")) {
    CDSGreeceHeadlines <- CDSGreeceWebsite %>% html_nodes(CDSGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (CDSGreeceHeadline in CDSGreeceHeadlines) {
      GreeceItalianVectorOfWordsMatch <- any(str_detect(CDSGreeceHeadline, regex(paste(GreeceItalianVectorOfWords, collapse = "|"),
                                                         ignore_case = TRUE)))
      
      if (GreeceItalianVectorOfWordsMatch) {
        CDSGreeceRawWeighting <-
          length(CDSGreeceHeadlines) - match(CDSGreeceHeadline,
                                              CDSGreeceHeadlines) + 1
        CDSGreeceNormalisedWeighting <- CDSGreeceRawWeighting / length(CDSGreeceHeadlines) 

        if (CDSGreeceNormalisedWeighting > CDSGreeceMaxWeighting) {
          CDSGreeceMaxWeighting <- CDSGreeceNormalisedWeighting
          CDSGreeceMaxWeightingRow <- data.frame(CDSGreeceDate =
                                                    as.character(CurrentDateGreece),
                                                   CDSGreeceHeadline =
                                                    CDSGreeceHeadline,
                                                   CDSGreeceWeighting = 
                                                    CDSGreeceNormalisedWeighting, 
                                                   CDSGreeceTag = CDSGreeceTag)
        }
      }
    }
  }
  
  if (!is.null(CDSGreeceMaxWeightingRow)) {
    CDSGreeceDynamicDataFrame <- rbind(CDSGreeceDynamicDataFrame, CDSGreeceMaxWeightingRow)
  } else {
    CDSGreeceNARow <-
      data.frame(CDSGreeceDate = as.character(CurrentDateGreece),
                                   CDSGreeceHeadline = NA,
                                   CDSGreeceWeighting = 0,
                                   CDSGreeceTag = NA)
    CDSGreeceDynamicDataFrame <- rbind(CDSGreeceDynamicDataFrame,
                                         CDSGreeceNARow)
  }
}

head(CDSGreeceDynamicDataFrame)
tail(CDSGreeceDynamicDataFrame)

```

```{r}

write.xlsx(CDSGreeceDynamicDataFrame, "CorriereGreece2015.xlsx")

```


1.4.1 La Repubblica (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyLRGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  LRGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  LRGreeceOutputList <- fromJSON(content(LRGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(LRGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(LRGreeceOutputList) || ncol(LRGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- LRGreeceOutputList[1, ]
  LRGreeceHeadlines <- as.data.frame(LRGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(LRGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(LRGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredLRGreeceHeadlines <- LRGreeceHeadlines[
    substr(LRGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredLRGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidLRGreeceHeadlines <- FilteredLRGreeceHeadlines[
    FilteredLRGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredLRGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidLRGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidLRGreeceHeadlines)) {
    RandomLRGreeceHeadline <- ValidLRGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomLRGreeceHeadline$timestamp
    OriginalLRGreeceURL <- RandomLRGreeceHeadline$urlkey
    
    RegularLRGreeceURL <- gsub("it,repubblica)/", "repubblica.it/", OriginalLRGreeceURL, fixed = TRUE) 
    
    RetrievedLRGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularLRGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedLRGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from LR:", RetrievedLRGreeceURL, "\n")
      return(RetrievedLRGreeceURL)
    } else {
      cat("Snapshot", RetrievedLRGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreeceItalianVectorOfWords <- c("grec")

LRGreeceDynamicDataFrame <- data.frame(
  LRGreeceDate = character(0),
  LRGreeceHeadline = character(0),
  LRGreeceWeighting = numeric(0),
  LRGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  LRGreeceTargetURL <- DailyLRGreeceHeadline("www.repubblica.it", CurrentDateGreece) 
  
  if (is.na(LRGreeceTargetURL)) next
  
  LRGreeceWebsite <- read_html(LRGreeceTargetURL)
  
  LRGreeceMaxWeighting <- 0
  LRGreeceMaxWeightingRow <- NULL
  
  for (LRGreeceTag in c("h1", "h2", "h3")) {
    LRGreeceHeadlines <- LRGreeceWebsite %>% html_nodes(LRGreeceTag) %>% html_text(trim = TRUE)
    
    for (LRGreeceHeadline in LRGreeceHeadlines) {
      if (any(str_detect(LRGreeceHeadline, regex(paste(GreeceItalianVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        LRGreeceRawWeighting <- length(LRGreeceHeadlines) - match(LRGreeceHeadline, LRGreeceHeadlines) + 1
        LRGreeceNormalisedWeighting <- LRGreeceRawWeighting / length(LRGreeceHeadlines)
        
        if (LRGreeceNormalisedWeighting > LRGreeceMaxWeighting) {
          LRGreeceMaxWeighting <- LRGreeceNormalisedWeighting
          LRGreeceMaxWeightingRow <- data.frame(
            LRGreeceDate = as.character(CurrentDateGreece),
            LRGreeceHeadline = LRGreeceHeadline,
            LRGreeceWeighting = LRGreeceNormalisedWeighting,
            LRGreeceTag = LRGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(LRGreeceMaxWeightingRow)) {
    LRGreeceDynamicDataFrame <- rbind(LRGreeceDynamicDataFrame, LRGreeceMaxWeightingRow)
  } else {
    LRGreeceNARow <- data.frame(
      LRGreeceDate = as.character(CurrentDateGreece),
      LRGreeceHeadline = NA,
      LRGreeceWeighting = 0,
      LRGreeceTag = NA
    )
    LRGreeceDynamicDataFrame <- rbind(LRGreeceDynamicDataFrame, LRGreeceNARow)
  }
}

head(LRGreeceDynamicDataFrame)
tail(LRGreeceDynamicDataFrame)

```

```{r}

write.xlsx(LRGreeceDynamicDataFrame, "RepubblicaGreece2011.xlsx")

```


1.4.2 La Repubblica (2015)

```{r}

StartDateGreece <- as.Date("2015-01-27")

DailyLRGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  LRGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
                query = list(url = domain, timestamp = format(date, "%Y%m%d"),
                             output = "json"), times = 90, pause_cap = RandomPauseCap)
  
  LRGreeceOutputList <-
    fromJSON(content(LRGreeceOutputURL, "text", encoding = "UTF-8"))
  
  LRGreeceHeadlines <- as.data.frame(LRGreeceOutputList[-1, ],
                                       stringsAsFactors = FALSE)
  
  colnames(LRGreeceHeadlines) <- LRGreeceOutputList[1, ]
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredLRGreeceHeadlines <-
  LRGreeceHeadlines[grepl(DesiredDateGreece, LRGreeceHeadlines$timestamp,
                                  fixed = TRUE), ]
  
  RandomLRGreeceHeadline <-
    FilteredLRGreeceHeadlines[sample(1:nrow(FilteredLRGreeceHeadlines), 1), ]
  
  TimestampGreece <- RandomLRGreeceHeadline$timestamp
  
  OriginalLRGreeceURL <- RandomLRGreeceHeadline$urlkey
  
  RegularLRGreeceURL <- gsub("it,repubblica)/", "repubblica.it/",
                                OriginalLRGreeceURL, fixed = TRUE) 
  
  RetrievedLRGreeceURL <- paste0("https://web.archive.org/web/",
                                   TimestampGreece, "/",
                                    RegularLRGreeceURL)
  
  cat("Retrieved from Repubblica:", RetrievedLRGreeceURL, "\n")
  
  return(RetrievedLRGreeceURL)
}

GreeceItalianVectorOfWords <- c("grec")

LRGreeceDynamicDataFrame <- data.frame(LRGreeceDate = character(0),
                                          LRGreeceHeadline = character(0),
                                          LRGreeceWeighting = numeric(0),
                                          LRGreeceTag = character(0))

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  LRGreeceTargetURL <- DailyLRGreeceHeadline("www.repubblica.it",
                                                   CurrentDateGreece) 
  
  LRGreeceWebsite <- read_html(LRGreeceTargetURL)
  
  LRGreeceMaxWeighting <- 0
  LRGreeceMaxWeightingRow <- NULL
  
  for (LRGreeceTag in c("h1", "h2", "h3")) {
    LRGreeceHeadlines <- LRGreeceWebsite %>% html_nodes(LRGreeceTag) %>%
      html_text(trim = TRUE)
    
    for (LRGreeceHeadline in LRGreeceHeadlines) {
      GreeceItalianVectorOfWordsMatch <- any(str_detect(LRGreeceHeadline, regex(paste(GreeceItalianVectorOfWords, collapse = "|"),
                                                         ignore_case = TRUE)))
      
      if (GreeceItalianVectorOfWordsMatch) {
        LRGreeceRawWeighting <-
          length(LRGreeceHeadlines) - match(LRGreeceHeadline,
                                              LRGreeceHeadlines) + 1
        LRGreeceNormalisedWeighting <- LRGreeceRawWeighting / length(LRGreeceHeadlines) 

        if (LRGreeceNormalisedWeighting > LRGreeceMaxWeighting) {
          LRGreeceMaxWeighting <- LRGreeceNormalisedWeighting
          LRGreeceMaxWeightingRow <- data.frame(LRGreeceDate =
                                                    as.character(CurrentDateGreece),
                                                   LRGreeceHeadline =
                                                    LRGreeceHeadline,
                                                   LRGreeceWeighting = 
                                                    LRGreeceNormalisedWeighting, 
                                                   LRGreeceTag = LRGreeceTag)
        }
      }
    }
  }
  
  if (!is.null(LRGreeceMaxWeightingRow)) {
    LRGreeceDynamicDataFrame <- rbind(LRGreeceDynamicDataFrame, LRGreeceMaxWeightingRow)
  } else {
    LRGreeceNARow <-
      data.frame(LRGreeceDate = as.character(CurrentDateGreece),
                                   LRGreeceHeadline = NA,
                                   LRGreeceWeighting = 0,
                                   LRGreeceTag = NA)
    LRGreeceDynamicDataFrame <- rbind(LRGreeceDynamicDataFrame,
                                         LRGreeceNARow)
  }
}

head(LRGreeceDynamicDataFrame)
tail(LRGreeceDynamicDataFrame)

```

```{r}

write.xlsx(LRGreeceDynamicDataFrame, "RepubblicaGreece2015.xlsx")

```


1.5.1 Publico (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyPublicoGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  PublicoGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  PublicoGreeceOutputList <- fromJSON(content(PublicoGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(PublicoGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(PublicoGreeceOutputList) || ncol(PublicoGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- PublicoGreeceOutputList[1, ]
  PublicoGreeceHeadlines <- as.data.frame(PublicoGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(PublicoGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(PublicoGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredPublicoGreeceHeadlines <- PublicoGreeceHeadlines[
    substr(PublicoGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredPublicoGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidPublicoGreeceHeadlines <- FilteredPublicoGreeceHeadlines[
    FilteredPublicoGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredPublicoGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidPublicoGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidPublicoGreeceHeadlines)) {
    RandomPublicoGreeceHeadline <- ValidPublicoGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomPublicoGreeceHeadline$timestamp
    OriginalPublicoGreeceURL <- RandomPublicoGreeceHeadline$urlkey
    
    RegularPublicoGreeceURL <- gsub("pt,publico)/", "publico.pt/", OriginalPublicoGreeceURL, fixed = TRUE) 
    
    RetrievedPublicoGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularPublicoGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedPublicoGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from Publico:", RetrievedPublicoGreeceURL, "\n")
      return(RetrievedPublicoGreeceURL)
    } else {
      cat("Snapshot", RetrievedPublicoGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreecePortugueseVectorOfWords <- c("grécia", "greg")

PublicoGreeceDynamicDataFrame <- data.frame(
  PublicoGreeceDate = character(0),
  PublicoGreeceHeadline = character(0),
  PublicoGreeceWeighting = numeric(0),
  PublicoGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  PublicoGreeceTargetURL <- DailyPublicoGreeceHeadline("www.publico.pt", CurrentDateGreece) 
  
  if (is.na(PublicoGreeceTargetURL)) next
  
  PublicoGreeceWebsite <- read_html(PublicoGreeceTargetURL)
  
  PublicoGreeceMaxWeighting <- 0
  PublicoGreeceMaxWeightingRow <- NULL
  
  for (PublicoGreeceTag in c("h1", "h2", "h3")) {
    PublicoGreeceHeadlines <- PublicoGreeceWebsite %>% html_nodes(PublicoGreeceTag) %>% html_text(trim = TRUE)
    
    for (PublicoGreeceHeadline in PublicoGreeceHeadlines) {
      if (any(str_detect(PublicoGreeceHeadline, regex(paste(GreecePortugueseVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        PublicoGreeceRawWeighting <- length(PublicoGreeceHeadlines) - match(PublicoGreeceHeadline, PublicoGreeceHeadlines) + 1
        PublicoGreeceNormalisedWeighting <- PublicoGreeceRawWeighting / length(PublicoGreeceHeadlines)
        
        if (PublicoGreeceNormalisedWeighting > PublicoGreeceMaxWeighting) {
          PublicoGreeceMaxWeighting <- PublicoGreeceNormalisedWeighting
          PublicoGreeceMaxWeightingRow <- data.frame(
            PublicoGreeceDate = as.character(CurrentDateGreece),
            PublicoGreeceHeadline = PublicoGreeceHeadline,
            PublicoGreeceWeighting = PublicoGreeceNormalisedWeighting,
            PublicoGreeceTag = PublicoGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(PublicoGreeceMaxWeightingRow)) {
    PublicoGreeceDynamicDataFrame <- rbind(PublicoGreeceDynamicDataFrame, PublicoGreeceMaxWeightingRow)
  } else {
    PublicoGreeceNARow <- data.frame(
      PublicoGreeceDate = as.character(CurrentDateGreece),
      PublicoGreeceHeadline = NA,
      PublicoGreeceWeighting = 0,
      PublicoGreeceTag = NA
    )
    PublicoGreeceDynamicDataFrame <- rbind(PublicoGreeceDynamicDataFrame, PublicoGreeceNARow)
  }
}

head(PublicoGreeceDynamicDataFrame)
tail(PublicoGreeceDynamicDataFrame)

```

```{r}

write.xlsx(PublicoGreeceDynamicDataFrame, "PublicoGreece2011.xlsx")

```


1.5.2 Publico (2015)

```{r}

StartDateGreece <- as.Date("2015-01-27")

DailyPublicoGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  PublicoGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  PublicoGreeceOutputList <- fromJSON(content(PublicoGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(PublicoGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(PublicoGreeceOutputList) || ncol(PublicoGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- PublicoGreeceOutputList[1, ]
  PublicoGreeceHeadlines <- as.data.frame(PublicoGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(PublicoGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(PublicoGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredPublicoGreeceHeadlines <- PublicoGreeceHeadlines[
    substr(PublicoGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredPublicoGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidPublicoGreeceHeadlines <- FilteredPublicoGreeceHeadlines[
    FilteredPublicoGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredPublicoGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidPublicoGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidPublicoGreeceHeadlines)) {
    RandomPublicoGreeceHeadline <- ValidPublicoGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomPublicoGreeceHeadline$timestamp
    OriginalPublicoGreeceURL <- RandomPublicoGreeceHeadline$urlkey
    
    RegularPublicoGreeceURL <- gsub("pt,publico)/", "publico.pt/", OriginalPublicoGreeceURL, fixed = TRUE) 
    
    RetrievedPublicoGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularPublicoGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedPublicoGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from Publico:", RetrievedPublicoGreeceURL, "\n")
      return(RetrievedPublicoGreeceURL)
    } else {
      cat("Snapshot", RetrievedPublicoGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreecePortugueseVectorOfWords <- c("grécia", "greg")

PublicoGreeceDynamicDataFrame <- data.frame(
  PublicoGreeceDate = character(0),
  PublicoGreeceHeadline = character(0),
  PublicoGreeceWeighting = numeric(0),
  PublicoGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(35, 60, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  PublicoGreeceTargetURL <- DailyPublicoGreeceHeadline("www.publico.pt", CurrentDateGreece) 
  
  if (is.na(PublicoGreeceTargetURL)) next
  
  PublicoGreeceWebsite <- read_html(PublicoGreeceTargetURL)
  
  PublicoGreeceMaxWeighting <- 0
  PublicoGreeceMaxWeightingRow <- NULL
  
  for (PublicoGreeceTag in c("h1", "h2", "h3")) {
    PublicoGreeceHeadlines <- PublicoGreeceWebsite %>% html_nodes(PublicoGreeceTag) %>% html_text(trim = TRUE)
    
    for (PublicoGreeceHeadline in PublicoGreeceHeadlines) {
      if (any(str_detect(PublicoGreeceHeadline, regex(paste(GreecePortugueseVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        PublicoGreeceRawWeighting <- length(PublicoGreeceHeadlines) - match(PublicoGreeceHeadline, PublicoGreeceHeadlines) + 1
        PublicoGreeceNormalisedWeighting <- PublicoGreeceRawWeighting / length(PublicoGreeceHeadlines)
        
        if (PublicoGreeceNormalisedWeighting > PublicoGreeceMaxWeighting) {
          PublicoGreeceMaxWeighting <- PublicoGreeceNormalisedWeighting
          PublicoGreeceMaxWeightingRow <- data.frame(
            PublicoGreeceDate = as.character(CurrentDateGreece),
            PublicoGreeceHeadline = PublicoGreeceHeadline,
            PublicoGreeceWeighting = PublicoGreeceNormalisedWeighting,
            PublicoGreeceTag = PublicoGreeceTag
          )
        }
      }
    }
  }
  
  if (!is.null(PublicoGreeceMaxWeightingRow)) {
    PublicoGreeceDynamicDataFrame <- rbind(PublicoGreeceDynamicDataFrame, PublicoGreeceMaxWeightingRow)
  } else {
    PublicoGreeceNARow <- data.frame(
      PublicoGreeceDate = as.character(CurrentDateGreece),
      PublicoGreeceHeadline = NA,
      PublicoGreeceWeighting = 0,
      PublicoGreeceTag = NA
    )
    PublicoGreeceDynamicDataFrame <- rbind(PublicoGreeceDynamicDataFrame, PublicoGreeceNARow)
  }
}

head(PublicoGreeceDynamicDataFrame)
tail(PublicoGreeceDynamicDataFrame)

```

```{r}

write.xlsx(PublicoGreeceDynamicDataFrame, "PublicoGreece2015.xlsx")

```


1.6.1 Irish Times (2011)

```{r}

StartDateGreece <- as.Date("2011-05-25")

DailyITGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ITGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  ITGreeceOutputList <- fromJSON(content(ITGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(ITGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(ITGreeceOutputList) || ncol(ITGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- ITGreeceOutputList[1, ]
  ITGreeceHeadlines <- as.data.frame(ITGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(ITGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(ITGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredITGreeceHeadlines <- ITGreeceHeadlines[
    substr(ITGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredITGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidITGreeceHeadlines <- FilteredITGreeceHeadlines[
    FilteredITGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredITGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidITGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidITGreeceHeadlines)) {
    RandomITGreeceHeadline <- ValidITGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomITGreeceHeadline$timestamp
    OriginalITGreeceURL <- RandomITGreeceHeadline$urlkey
    
    RegularITGreeceURL <- gsub("com,irishtimes)/", "irishtimes.com/", OriginalITGreeceURL, fixed = TRUE) 
    
    RetrievedITGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularITGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedITGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from IT:", RetrievedITGreeceURL, "\n")
      return(RetrievedITGreeceURL)
    } else {
      cat("Snapshot", RetrievedITGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreeceEnglishVectorOfWords <- c("Greece", "greek")

ITGreeceDynamicDataFrame <- data.frame(
  ITGreeceDate = character(0),
  ITGreeceHeadline = character(0),
  ITGreeceWeighting = numeric(0),
  ITGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(15, 30, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ITGreeceTargetURL <- DailyITGreeceHeadline("www.irishtimes.com", CurrentDateGreece) 
  
  if (is.na(ITGreeceTargetURL)) next
  
  ITGreeceWebsite <- read_html(ITGreeceTargetURL)
  
  ITGreeceMaxWeighting <- 0
  ITGreeceMaxWeightingRow <- NULL
  
  for (ITGreeceTag in c("h1", "h2", "h3")) {
    ITGreeceHeadlines <- ITGreeceWebsite %>% html_nodes(paste0("span.", ITGreeceTag)) %>% html_text(trim = TRUE)
    
    if (length(ITGreeceHeadlines) == 0) next
    
    for (ITGreeceHeadline in ITGreeceHeadlines) {
      if (any(str_detect(ITGreeceHeadline, regex(paste(GreeceEnglishVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        ITGreeceRawWeighting <- length(ITGreeceHeadlines) - match(ITGreeceHeadline, ITGreeceHeadlines) + 1
        ITGreeceNormalisedWeighting <- ITGreeceRawWeighting / length(ITGreeceHeadlines)
        
        if (ITGreeceNormalisedWeighting > ITGreeceMaxWeighting) {
          ITGreeceMaxWeighting <- ITGreeceNormalisedWeighting
          ITGreeceMaxWeightingRow <- data.frame(
            ITGreeceDate = as.character(CurrentDateGreece),
            ITGreeceHeadline = ITGreeceHeadline,
            ITGreeceWeighting = ITGreeceNormalisedWeighting,
            ITGreeceTag = ITGreeceTag
          )
        }
      }
    }
  }
  
  ITGreeceDynamicDataFrame <- rbind(ITGreeceDynamicDataFrame, ITGreeceMaxWeightingRow)
}

head(ITGreeceDynamicDataFrame)
tail(ITGreeceDynamicDataFrame)

```

```{r}

write.xlsx(ITGreeceDynamicDataFrame, "IrishTimesGreece2011.xlsx")

```


1.6.2 Irish Times (2015)

```{r}

StartDateGreece <- as.Date("2015-01-27")

DailyITGreeceHeadline <- function(domain, date) {
  Sys.sleep(sample(seq(22.5, 35, by = 0.1), 1))
  RandomPauseCap <- sample(seq(25, 55, by = 0.1), 1)
  WebArchiveURL <- "http://web.archive.org/cdx/search/cdx?url="
  
  ITGreeceOutputURL <-
    RETRY("GET", WebArchiveURL, timeout(sample(seq(60, 120, by = 0.1), 1)),
          query = list(url = domain, 
                       from = format(date, "%Y%m%d"), 
                       to = format(date + days(1), "%Y%m%d"), 
                       output = "json"), 
          times = 90, pause_cap = RandomPauseCap)
  
  ITGreeceOutputList <- fromJSON(content(ITGreeceOutputURL, "text", encoding = "UTF-8"))
  
  if (length(ITGreeceOutputList) <= 1) {
    cat("No snapshots available for", date, "\n")
    return(NA)
  }
  
  if (!is.matrix(ITGreeceOutputList) || ncol(ITGreeceOutputList) < 7) {
    cat("Unexpected API response structure for", date, "\n")
    return(NA)
  }
  
  ColumnNames <- ITGreeceOutputList[1, ]
  ITGreeceHeadlines <- as.data.frame(ITGreeceOutputList[-1, ], stringsAsFactors = FALSE)
  
  if (length(ColumnNames) != ncol(ITGreeceHeadlines)) {
    cat("Column names do not match the number of columns for", date, "\n")
    return(NA)
  }
  
  colnames(ITGreeceHeadlines) <- ColumnNames
  
  DesiredDateGreece <- format(date, "%Y%m%d")
  
  FilteredITGreeceHeadlines <- ITGreeceHeadlines[
    substr(ITGreeceHeadlines$timestamp, 1, 8) == DesiredDateGreece, ]
  
  if (nrow(FilteredITGreeceHeadlines) == 0) {
    cat("No valid headlines found for", date, "\n")
    return(NA)
  }
  
  ValidITGreeceHeadlines <- FilteredITGreeceHeadlines[
    FilteredITGreeceHeadlines$mimetype != "warc/revisit" & 
    FilteredITGreeceHeadlines$statuscode != "301", ]
  
  if (nrow(ValidITGreeceHeadlines) == 0) {
    cat("No valid content snapshots available for", date, "\n")
    return(NA)
  }
  
  for (attempt in 1:nrow(ValidITGreeceHeadlines)) {
    RandomITGreeceHeadline <- ValidITGreeceHeadlines[attempt, ]
    
    TimestampGreece <- RandomITGreeceHeadline$timestamp
    OriginalITGreeceURL <- RandomITGreeceHeadline$urlkey
    
    RegularITGreeceURL <- gsub("com,irishtimes)/", "irishtimes.com/", OriginalITGreeceURL, fixed = TRUE) 
    
    RetrievedITGreeceURL <- paste0("https://web.archive.org/web/",
                                    TimestampGreece, "/",
                                    RegularITGreeceURL)
    
    SnapshotCheck <- RETRY("GET", RetrievedITGreeceURL, timeout(10), times = 3)
    if (status_code(SnapshotCheck) == 200) {
      cat("Retrieved from IT:", RetrievedITGreeceURL, "\n")
      return(RetrievedITGreeceURL)
    } else {
      cat("Snapshot", RetrievedITGreeceURL, "is a redirect. Trying next snapshot...\n")
    }
  }
  
  cat("No valid snapshots found for", date, "\n")
  return(NA)
}

GreeceEnglishVectorOfWords <- c("Greece", "greek")

ITGreeceDynamicDataFrame <- data.frame(
  ITGreeceDate = character(0),
  ITGreeceHeadline = character(0),
  ITGreeceWeighting = numeric(0),
  ITGreeceTag = character(0)
)

for (i in 0:160) {
  Sys.sleep(sample(seq(15, 30, by = 0.1), 1)) 
  
  CurrentDateGreece <- StartDateGreece + days(i)
  ITGreeceTargetURL <- DailyITGreeceHeadline("www.irishtimes.com", CurrentDateGreece) 
  
  if (is.na(ITGreeceTargetURL)) next
  
  ITGreeceWebsite <- read_html(ITGreeceTargetURL)
  
  ITGreeceMaxWeighting <- 0
  ITGreeceMaxWeightingRow <- NULL
  
  for (ITGreeceTag in c("h1", "h2", "h3")) {
    ITGreeceHeadlines <- ITGreeceWebsite %>% html_nodes(paste0("span.", ITGreeceTag)) %>% html_text(trim = TRUE)
    
    if (length(ITGreeceHeadlines) == 0) next
    
    for (ITGreeceHeadline in ITGreeceHeadlines) {
      if (any(str_detect(ITGreeceHeadline, regex(paste(GreeceEnglishVectorOfWords, collapse = "|"), ignore_case = TRUE)))) {
        ITGreeceRawWeighting <- length(ITGreeceHeadlines) - match(ITGreeceHeadline, ITGreeceHeadlines) + 1
        ITGreeceNormalisedWeighting <- ITGreeceRawWeighting / length(ITGreeceHeadlines)
        
        if (ITGreeceNormalisedWeighting > ITGreeceMaxWeighting) {
          ITGreeceMaxWeighting <- ITGreeceNormalisedWeighting
          ITGreeceMaxWeightingRow <- data.frame(
            ITGreeceDate = as.character(CurrentDateGreece),
            ITGreeceHeadline = ITGreeceHeadline,
            ITGreeceWeighting = ITGreeceNormalisedWeighting,
            ITGreeceTag = ITGreeceTag
          )
        }
      }
    }
  }
  
  ITGreeceDynamicDataFrame <- rbind(ITGreeceDynamicDataFrame, ITGreeceMaxWeightingRow)
}

head(ITGreeceDynamicDataFrame)
tail(ITGreeceDynamicDataFrame)

```

```{r}

write.xlsx(ITGreeceDynamicDataFrame, "IrishTimesGreece2015.xlsx")

```


***Part II - Sentiment and Frequency Analysis***

2.1.1 El País (2011)

```{r}

ElPais2011 <- read_excel("CleanElPaisGreece2011.xlsx")

ElPais2011Sentiment <- get_sentiment(ElPais2011$ElPaisHeadline, method = "nrc", language = "spanish")

head(ElPais2011Sentiment)

summary(ElPais2011Sentiment)

hist(ElPais2011Sentiment, breaks = 20, col = "forestgreen",
     main = "Sentiment Distribution in El País (2011) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

ElPais2011OverallSentiment <- mean(ElPais2011Sentiment)
print(paste("Overall Sentiment Score for El País (2011):", ElPais2011OverallSentiment))

ElPais2011Emotions <- get_nrc_sentiment(ElPais2011$ElPaisHeadline, language = "spanish")
print(ElPais2011Emotions)

barplot(colSums(ElPais2011Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in El País (2011) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.24


2.1.2 El País (2015)

```{r}

ElPais2015 <- read_excel("CleanElPaisGreece2015.xlsx")

ElPais2015Sentiment <- get_sentiment(ElPais2015$ElPaisHeadline, method = "nrc", language = "spanish")

head(ElPais2015Sentiment)

summary(ElPais2015Sentiment)

hist(ElPais2015Sentiment, breaks = 20, col = "forestgreen",
     main = "Sentiment Distribution in El País (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

ElPais2015OverallSentiment <- mean(ElPais2015Sentiment)
print(paste("Overall Sentiment Score for El País (2015):", ElPais2015OverallSentiment))

ElPais2015Emotions <- get_nrc_sentiment(ElPais2015$ElPaisHeadline, language = "spanish")
print(ElPais2015Emotions)

barplot(colSums(ElPais2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in El País (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.29


2.2.1 El Mundo (2011)

```{r}

ElMundo2011 <- read_excel("CleanElMundoGreece2011.xlsx")

ElMundo2011Sentiment <- get_sentiment(ElMundo2011$ElMundoHeadline, method = "nrc", language = "spanish")

head(ElMundo2011Sentiment)

summary(ElMundo2011Sentiment)

hist(ElMundo2011Sentiment, breaks = 20, col = "steelblue",
     main = "Sentiment Distribution in El Mundo (2011) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

ElMundo2011OverallSentiment <- mean(ElMundo2011Sentiment)
print(paste("Overall Sentiment Score for El Mundo (2011):", ElMundo2011OverallSentiment))

ElMundo2011Emotions <- get_nrc_sentiment(ElMundo2011$ElMundoHeadline, language = "spanish")
print(ElMundo2011Emotions)

barplot(colSums(ElMundo2011Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in El Mundo (2011) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.05


2.2.2 El Mundo (2015)

```{r}

ElMundo2015 <- read_excel("CleanElMundoGreece2015.xlsx")

ElMundo2015Sentiment <- get_sentiment(ElMundo2015$ElMundoHeadline, method = "nrc", language = "spanish")

head(ElMundo2015Sentiment)

summary(ElMundo2015Sentiment)

hist(ElMundo2015Sentiment, breaks = 20, col = "steelblue",
     main = "Sentiment Distribution in El Mundo (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

ElMundo2015OverallSentiment <- mean(ElMundo2015Sentiment)
print(paste("Overall Sentiment Score for El Mundo (2015):", ElMundo2015OverallSentiment))

ElMundo2015Emotions <- get_nrc_sentiment(ElMundo2015$ElMundoHeadline, language = "spanish")
print(ElMundo2015Emotions)

barplot(colSums(ElMundo2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in El Mundo (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.20


2.3 Corriere della Serra (2015)

```{r}

Corriere2015 <- read_excel("CleanCorriereGreece2015.xlsx")

Corriere2015Sentiment <- get_sentiment(Corriere2015$CDSHeadline, method = "nrc", language = "italian")

head(Corriere2015Sentiment)

summary(Corriere2015Sentiment)

hist(Corriere2015Sentiment, breaks = 20, col = "palegreen",
     main = "Sentiment Distribution in Corriere della Sera (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

Corriere2015OverallSentiment <- mean(Corriere2015Sentiment)
print(paste("Overall Sentiment Score for Corriere della Sera (2015):", Corriere2015OverallSentiment))

Corriere2015Emotions <- get_nrc_sentiment(Corriere2015$CDSHeadline, language = "italian")
print(Corriere2015Emotions)

barplot(colSums(Corriere2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in Corriere della Sera (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.02


2.4 La Repubblica (2015)

```{r}

Repubblica2015 <- read_excel("CleanRepubblicaGreece2015.xlsx")

Repubblica2015Sentiment <- get_sentiment(Repubblica2015$LRHeadline, method = "nrc", language = "italian")

head(Repubblica2015Sentiment)

summary(Repubblica2015Sentiment)

hist(Repubblica2015Sentiment, breaks = 20, col = "gray",
     main = "Sentiment Distribution in La Repubblica (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

Repubblica2015OverallSentiment <- mean(Repubblica2015Sentiment)
print(paste("Overall Sentiment Score for La Repubblica (2015):", Repubblica2015OverallSentiment))

Repubblica2015Emotions <- get_nrc_sentiment(Repubblica2015$LRHeadline, language = "italian")
print(Repubblica2015Emotions)

barplot(colSums(Repubblica2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in La Repubblica (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: 0.01


2.5.1 Publico (2011)

```{r}

Publico2011 <- read_excel("CleanPublicoGreece2011.xlsx")

Publico2011Sentiment <- get_sentiment(Publico2011$PublicoHeadline, method = "nrc", language = "portuguese")

head(Publico2011Sentiment)

summary(Publico2011Sentiment)

hist(Publico2011Sentiment, breaks = 20, col = "darkred",
     main = "Sentiment Distribution in Publico (2011) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

Publico2011OverallSentiment <- mean(Publico2011Sentiment)
print(paste("Overall Sentiment Score for Publico (2011):", Publico2011OverallSentiment))

Publico2011Emotions <- get_nrc_sentiment(Publico2011$PublicoHeadline, language = "portuguese")
print(Publico2011Emotions)

barplot(colSums(Publico2011Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in Publico (2011) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.04


2.5.2 Publico (2015)

```{r}

Publico2015 <- read_excel("CleanPublicoGreece2015.xlsx")

Publico2015Sentiment <- get_sentiment(Publico2015$PublicoHeadline, method = "nrc", language = "portuguese")

head(Publico2015Sentiment)

summary(Publico2015Sentiment)

hist(Publico2015Sentiment, breaks = 20, col = "darkred",
     main = "Sentiment Distribution in Publico (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

Publico2015OverallSentiment <- mean(Publico2015Sentiment)
print(paste("Overall Sentiment Score for Publico (2015):", Publico2015OverallSentiment))

Publico2015Emotions <- get_nrc_sentiment(Publico2015$PublicoHeadline, language = "portuguese")
print(Publico2015Emotions)

barplot(colSums(Publico2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in Publico (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.19


2.6.1 Irish Times (2011)

```{r}

IT2011 <- read_excel("IrishTimesGreece2011.xlsx")

IT2011Sentiment <- get_sentiment(IT2011$ITGreeceHeadline, method = "nrc", language = "english")

head(IT2011Sentiment)

summary(IT2011Sentiment)

hist(IT2011Sentiment, breaks = 20, col = "black",
     main = "Sentiment Distribution in Irish Times (2011) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

IT2011OverallSentiment <- mean(IT2011Sentiment)
print(paste("Overall Sentiment Score for Irish Times (2011):", IT2011OverallSentiment))

IT2011Emotions <- get_nrc_sentiment(IT2011$ITGreeceHeadline, language = "english")
print(IT2011Emotions)

barplot(colSums(IT2011Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in Irish Times (2011) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.16


2.6.2 Irish Times (2015)

```{r}

IT2015 <- read_excel("IrishTimesGreece2015.xlsx")

IT2015Sentiment <- get_sentiment(IT2015$ITGreeceHeadline, method = "nrc", language = "english")

head(IT2015Sentiment)

summary(IT2015Sentiment)

hist(IT2015Sentiment, breaks = 20, col = "black",
     main = "Sentiment Distribution in Irish Times (2015) Headlines",
     xlab = "Sentiment Score", ylab = "Frequency")

IT2015OverallSentiment <- mean(IT2015Sentiment)
print(paste("Overall Sentiment Score for Irish Times (2015):", IT2015OverallSentiment))

IT2015Emotions <- get_nrc_sentiment(IT2015$ITGreeceHeadline, language = "english")
print(IT2015Emotions)

barplot(colSums(IT2015Emotions), las = 2, col = rainbow(10),
        main = "Emotion Distribution in Irish Times (2015) Headlines",
        ylab = "Frequency", xlab = "Emotions")

```
Sentiment score: -0.04
